---
title: '[2]data_exploration'
author: "Wyliena Guan"
date: "6/28/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# load libraries and data ----
library(stringr)
library(ggplot2)
library(tidyr)
library(dplyr)

# data directory
setwd("/data/arrhythmia_source/data/PRESTO/presto rpdr 20180719")

# code directory
# setwd("/data/arrhythmia/wguan/cardioembolic_stroke/src")
# setwd("/data/arrhythmia/lubitz/af_rpdr_scripts/af_scripts_20190419/")

# report directory
# setwd("/data/arrhythmia/wguan/cardioembolic_stroke/analysis/report")

# load(file="/data/arrhythmia_source/data/PRESTO/presto rpdr 20180719/feature_table_wide.RData")
# load(file="/data/arrhythmia/wguan/cardioembolic_stroke/data/feature_table_wide4.RData")
load(file="/data/arrhythmia/wguan/cardioembolic_stroke/data/includeOtherStroke/feature_table_wide4.RData")
```

```{r}
# number of patients without any qualifying CE features (0 patients)
sum(is.na(feature_table_wide4$EMPI))
length(feature_table_wide4$EMPI)-sum(is.na(feature_table_wide4$EMPI))
```


```{r one_feature_freq}
# exclude variables v1, v2, v3
features_only <- feature_table_wide4
myvars <- names(feature_table_wide4) %in% c("EMPI", "MRN", "stroke_date_index", 
                                            "Toast", "CCS","Toast_new","Toast_final",
                                           "age","Gender","gender") #remove missing cardiac sources, response variables (TOAST, CCS)
features_only <- feature_table_wide4[!myvars]

freq_one_feature <- colSums(features_only, na.rm = T, dims = 1)
# freq_one_feature <- data.frame(feature = names(freq_one_feature), freq=freq_one_feature)

knitr::kable(freq_one_feature, digits = 6, format.args = list(big.mark = ",")) # Nicer view

barplot(sort(freq_one_feature, decreasing = T), main="Feature Frequency", 
        las=2)

# rect
# points
# x-axis
# y-axis
# lines
```
Legend:
cov	        cov.long
mech_valve	Mechanical prosthetic valve bioprosthetic or mechanical valve
ms	        Mitral stenosis
af	        Atrial fibrillation (other than lone atrial fibrillation)
laa	        Left atrial/atrial appendage thrombus (or smoke)
sss	        Sick sinus syndrome
mi_recent	  Recent myocardial infarction (<4weeks)
lvt	        Left ventricular thrombus (or smoke)
dc	        Dilated cardiomyopathy
akine_lvs	  Akinetic left ventricular segment
amyxoma	    Atrial myxoma
infect_ec	  Infective Endocarditis
mvp	        Mitral valve prolapse
mac	        Mitral annulus calcification
ms_noaf	    Mitral stenosis without atrial fibrillation
lat	        Left atrial turbulence (smoke)
asa	        Atrial septal aneurysm
pfo	        Patent foramen ovale
afl	        Atrial flutter
lone_af	    Lone atrial fibrillation
bio_valve	  Bioprosthetic cardiac valve
nonbact_ec	Nonbacterial thrombotic endocarditis
chf	        Congestive heart failure
hypo_lvs	  Hypokinetic left ventricular segment
mi_later	  Myocardial infarction (>4 weeks, <6 months)
dev         Delayed emptying velocity
intracard_thromb Intracardiac thrombus

```{r correlation, echo=FALSE}
cor_mat <- cor(features_only[,!(names(features_only) %in% c('intracard_thromb'))])

colSums(cor_mat>0.4)
cor_mat>0.3
# get correlations between variables greater than 0.3
get_correlations <- function(test) {
  test1 <- data.frame(which(test == T, arr.ind=TRUE))
  test2 <- test1[test1$row != test1$col,]
  test2$cov1 <- str_replace(rownames(test2),"\\..*","")
  test2$cov2 <- names(features_only)[test2$col]
  test2$cov <- apply(cbind(test2$cov1, test2$cov2), 1, function(x) paste(sort(x), collapse=" "))
  test3 <- distinct(test2, cov,.keep_all = T)
  return(test3$cov)
}
# get correlations between variables greater than 0.3
corr0.5 <- get_correlations(cor_mat>0.5)
corr0.4 <- get_correlations(cor_mat>0.4)
corr0.3 <- get_correlations(cor_mat>0.3)
corr0.2 <- get_correlations(cor_mat>0.2)

# install.packages("corrplot", repos = "http://cran.cnr.berkeley.edu/")
library(corrplot)
res1 <- cor.mtest(features_only, conf.level = .95)

colnames(cor_mat) <- c(
  'Atrial fibrillation',
  'Atrial flutter',
  'Akinetic left ventricular segment',
  'Atrial myxoma',
  'Atrial septal aneurysm',
  'Congestive heart failure',
  'Dilated cardiomyopathy',
  'Delayed emptying velocity',
  'Hypokinetic left ventricular segment',
  'Infective endocarditis',
  'Left atrial appendage thrombus',
  'Left atrial turbulence',
  'Left ventricular thrombus',
  'Mitral annulus calcification',
  'Mechanical and bioprosthetic valve',
  'Myocardial infarction (older)',
  'Myocardial infarction (recent)',
  'Mitral stenosis',
  'Mitral valve prolapse',
  'Nonbacterial endocarditis',
  'Patent foramen ovale',
  'Sick sinus syndrome'
  )
rownames(cor_mat) <- c(
  'Atrial fibrillation',
  'Atrial flutter',
  'Akinetic left ventricular segment',
  'Atrial myxoma',
  'Atrial septal aneurysm',
  'Congestive heart failure',
  'Dilated cardiomyopathy',
  'Delayed emptying velocity',
  'Hypokinetic left ventricular segment',
  'Infective endocarditis',
  'Left atrial appendage thrombus',
  'Left atrial turbulence',
  'Left ventricular thrombus',
  'Mitral annulus calcification',
  'Mechanical and bioprosthetic valve',
  'Myocardial infarction (older)',
  'Myocardial infarction (recent)',
  'Mitral stenosis',
  'Mitral valve prolapse',
  'Nonbacterial endocarditis',
  'Patent foramen ovale',
  'Sick sinus syndrome'
  )

corrplot(cor_mat, p.mat = res1$p, insig = "label_sig", type = "upper", order = "original",
         sig.level = c(.001, .01, .05), pch.cex = .5, pch.col = "white", tl.col = "black", tl.srt = 45)

```
Correlation matrix shows no strong correlation > 0.5.
Correlation matrix shows a few correlations > 0.3 -
[1] "af chf"                   "chf hypo_lvs"            
[3] "dc hypo_lvs"              "mac ms"                  
[5] "mech_bio_valve mi_recent"

```{r correlation, echo=FALSE}
corrplot(cor_mat, type = "upper", order = "hclust", hclust.method = c("ward.D2"),
         tl.col = "black", tl.srt = 45)

```

See clusters of features together here...

PC1
pfo, asa, amyxoma, intracard_thromb, nonbact_ec -- seem to cluster together

PC2
mac, af, sss, dev, nonbact_ec -- seem to cluster together as as well

PC3
(dc, hypo_lvs, mi_recent, chf), mi_later, lvt, infect_ec, dev, laa, amyxoma -- seem to cluster together

```{r}
corrplot(cor_mat, type = "upper", order = "FPC", 
         tl.col = "black", tl.srt = 45)

```
first principal component order = organized by first prinicipal component scores

Results for first principal component order are same as for hierarchical clustering.

```{r freq_total_features}
features_only <- feature_table_wide4
myvars <- names(feature_table_wide4) %in% c("EMPI", "MRN", "stroke_date_index", 
                                            "Toast", "CCS","Toast_new","Toast_final",
                                           "age","Gender","gender") #remove missing cardiac sources, response variables (TOAST, CCS)
features_only <- feature_table_wide4[!myvars]

freq_total_features <- rowSums(features_only, na.rm = F, dims = 1)

data.frame(table(freq_total_features))
# aggregate(freq_total_features, by=list(feature_table_wide4$Toast_final))
# Table - baseline frequencies - number of features statified by CE
table(freq_total_features, feature_table_wide4$Toast_final)

a <- ggplot(as.data.frame(freq_total_features), aes(freq_total_features))
a + geom_histogram(bins=30) + 
  ggtitle("Histogram of Total Number of CE Features per Patient") +
  scale_x_continuous(name = " ", breaks = 1:10)
```

```{r freq_total_features}
features_only <- feature_table_wide4
myvars <- names(feature_table_wide4) %in% c("EMPI", "MRN", "stroke_date_index", 
                                            "Toast", "CCS","Toast_new","Toast_final",
                                           "age","Gender","gender") #remove missing cardiac sources, response variables (TOAST, CCS)
features_only <- feature_table_wide4[!myvars]

freq_total_features <- data.frame(count=as.numeric(rowSums(features_only, na.rm = F, dims = 1)))

freq_total_features$Toast_final <- as.factor(feature_table_wide4$Toast_final)

# freq_total_features <- data.frame(table(freq_total_features))
# aggregate(freq_total_features, by=list(feature_table_wide4$Toast_final))
# Table - baseline frequencies - number of features statified by CE
# table(freq_total_features, feature_table_wide4$Toast_final)


a <- ggplot(freq_total_features, aes(x=count, fill=as.factor(Toast_final))) +
  geom_histogram(aes(fill=as.factor(Toast_final)), alpha=0.4, position = "dodge2", binwidth = 0.5) +
  # geom_histogram(data=subset(freq_total_features,Toast_final==1), aes(fill=as.factor(Toast_final)), alpha=0.4) +
  scale_x_continuous(name = " ", breaks = 0:11) +
  scale_fill_manual(name="", values=c("green","red"), labels=c("Non-CE","CE")) +   
  xlab("Number of CE Features") +
  ylab("Frequency") +
  ggtitle("Total Number of CE Features per Patient") +
  theme(legend.position = "bottom", 
        plot.title = element_text(hjust = 0.5, family="Arial"))
a

```
```{r summary_total_features}
summary(freq_total_features)
```
Mean number of features = 1.549
Median number of features = 2

```{r combo_features_freq}
# exclude variables v1, v2, v3
features_only <- feature_table_wide4
myvars <- names(feature_table_wide4) %in% c("EMPI", "stroke_date_index", "Toast", "CCS", "Toast_new", "Toast_final", "age", "Gender", "gender") #remove missing cardiac sources, response variables (TOAST, CCS)
features_only <- feature_table_wide4[!myvars]
logic <- feature_table_wide4$Toast_final == 1
features_only <- feature_table_wide4[logic,!myvars]

combos <- features_only %>% unite(combo,sep = "", remove = F)
combos <- combos %>% dplyr::select(combo) %>% unlist()
combos_freq <- table(combos)
combos_freq <- as.data.frame(sort(combos_freq, decreasing = T))

names(features_only)

get_combo_name <- function(combos) {
  combo_name = paste(names(features_only)[str_locate_all(as.character(combos),'1')[[1]]],"")

  location_ones <- sapply(as.character(combos), function (x) {str_locate_all(x,'1')}, simplify = T)
  string_ones <- sapply(location_ones, function(x) {paste(names(features_only)[x[,1]],collapse=" ") })
  # count_ones <- sapply(location_ones, function(x) {length(x[,1])})
  
  # combos_freq$combo_name <- string_ones
  return(string_ones)
}

combo_name = paste(names(features_only)[str_locate_all(as.character(combos_freq$combos),'1')[[1]]],"")

location_ones <- sapply(as.character(combos_freq$combos), function (x) {str_locate_all(x,'1')}, simplify = T)
string_ones <- sapply(location_ones, function(x) {paste(names(features_only)[x[,1]],collapse=" ") })
count_ones <- sapply(location_ones, function(x) {length(x[,1])})

combos_freq$combo_name <- string_ones; combos_freq$features_cnt <- count_ones
rm(location_ones, string_ones)
sum(combos_freq$Freq) # 1090
combos_freq[,c('Freq','combo_name')]
sum(combos_freq[,c('Freq')])
dim(combos_freq)
sum(features_only[,c('af')])/355

```
(1090-267)/1090 = 75.5% have at least 1 TOAST feature


```{r}
combos_freq_vec <- as.vector(combos_freq$Freq)
sum(combos_freq_vec)

```

```{r examine toast_final==1, af subgroup}
features_only <- feature_table_wide4
myvars <- names(feature_table_wide4) %in% c("EMPI", "stroke_date_index", "Toast", "CCS", "Toast_new", "age", "Gender", "gender") #remove missing cardiac sources, response variables (TOAST, CCS)
features_only <- feature_table_wide4[!myvars]
logic <- feature_table_wide4$Toast_final == 1

ce_af_freq <- features_only %>% filter(Toast_final == 1) %>%
  filter(af == 1) %>% colSums() %>% data.frame()

ce_af_freq$feature <- row.names(ce_af_freq)

ce_af_freq %>% arrange(desc(.))
```

```{r}
# cardioembolic stroke data table
table(feature_table_wide4$Gender)
prop.table(table(feature_table_wide4$Gender))

summary(as.numeric(feature_table_wide4$age))

hist(as.numeric(feature_table_wide4[feature_table_wide4$Gender=="Female",]$age))
hist(as.numeric(feature_table_wide4[feature_table_wide4$Gender=="Male",]$age))
```

```{r generate_QC}
# add column (freq_total_features)
feature_table_wide_sample <- feature_table_wide4
feature_table_wide_sample$total_features <- freq_total_features

# 747 patients with features

# get sample of XX (e.g. 50) patients
set.seed(22)
feature_table_wide_sample <- feature_table_wide_sample[sample(1:nrow(feature_table_wide_sample), replace=F),] %>%  top_n(n=32, wt=total_features)
# skewed towards patients with greater number of features
# 39 or 92

# do a chart review for patients using their MRNs using data up until 2 weeks before date of RPDR pull

```

```{r}
# Remove Toast column, add mrns back to na.omit(feature_table_wide) as row name
# exclude variables
myvars <- names(feature_table_wide4) %in% c("EMPI","stroke_date_index","Toast","CCS",
                                           "Toast_new","Toast_final","age","Gender",
                                           "gender") 
features_Toast <- feature_table_wide4[!myvars]

df = as.matrix(features_Toast)

# retrieve PC directions U_j {j = 1,..., 4431}
sample_cov <- cov(df)
eigen_results = eigen(sample_cov)

```


```{r}
##### PART A #####
# project each article onto a subpace with 1-3 dim
# using PC directions W_1, W_2, W_3
# Project onto PC1
X = eigen_results$vectors[,c(1)]
P = solve(t(X) %*% X) %*% t(X)

Prjtns = as.data.frame(t(as.matrix(P %*% t(as.matrix(df)))))
Prjtns_class = cbind(Prjtns, class = feature_table_wide4$Toast)
(ggplot(data = Prjtns_class, aes(x = V1, y = 0)) + geom_point(aes(color=class))
+ labs(title = "Projection onto PC1", x = "PC1"))
```

```{r}
# Project onto PC1, PC2
X = eigen_results$vectors[,c(1, 2)]
P = solve(t(X) %*% X) %*% t(X)
Prjtns = as.data.frame(t(as.matrix(P %*% t(as.matrix(df)))))
Prjtns_class = cbind(Prjtns, class = feature_table_wide4$Toast_final)
(ggplot(data = Prjtns_class, aes(x = V1, y = V2)) + geom_point(aes(color=class))
+ labs(title = "Projection onto PC1 and PC2", x = "PC1", y = "PC2"))
```

```{r}
library(plotly)
# Project onto PC1, PC2, PC3
X = eigen_results$vectors[,c(1, 2, 3)]
P = solve(t(X) %*% X) %*% t(X)
Prjtns = as.data.frame(t(as.matrix(P %*% t(as.matrix(df)))))
Prjtns_class = cbind(Prjtns, class = feature_table_wide4$Toast_final)
plot_ly(x=Prjtns_class$V1, y=Prjtns_class$V2, z=Prjtns_class$V3, type="scatter3d", mode="markers", color=feature_table_wide4$Toast_final)
```
Cardioembolic vs. non-cardioembolic points overlap a lot


```{r}
##### PART B #####
# Examine the weights/loadings of each W_j can give us some insight
# about the roles of original variables (dimensions)

# how much variation captured
sum(eigen_results$values[c(1:3)])/sum(eigen_results$values)

weights = eigen_results$values[c(1,2,3)]^0.5
weights = diag(weights)
X = eigen_results$vectors[,c(1,2,3)]
X = X %*% weights
X = as.data.frame(X)
X$word = colnames(df)

# !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
# Report the 20 words which correspond to the maximum positive
# and minimum negative weights for each of the top 3 PC directions.
X_wt1 <- X[order(-X$V1),]
head(X_wt1[c("word")], 20)

X_wt2 <- X[order(-X$V2),]
head(X_wt2[c("word")], 20)

X_wt3 <- X[order(-X$V3),]
head(X_wt3[c("word")], 20)
```
PC1
pfo, asa, intracard_thromb, nonbact_ec, amyxoma  -- seem to cluster together

PC2
mac, sss, dev, intracard_thromb, dev, nonbact_ec -- seem to cluster together as as well

PC3
mac, pfo, akine_lvs, ms, asa -- seem to cluster together


```{r}
# !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
# Based on this, can you comment on the role each of the PC direction
# play in capturing the variation (variance) of the data set of articles?
# &gt; From the principal component, you get a list of words that appear
# the most often or least often in an article together for some reason.
# Usually, the words would gather around together to express a particular
# topic such as music or art.
# These words could capture the "heart" of the meaning in the article, so to speak.
# !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
##### part c #####
# Perform Kernel PCA with polynomial and Gaussian kernels
normalizeK <- function(K) {
  n = dim(K)[1]
  A = (diag(n) - 1/n * matrix(1, nrow = n, ncol = 1) %*%
  matrix(1, nrow = 1, ncol = n))
  ret <- A %*% K %*% A
  return(ret)
}
# define kernels
plainK <- function(x) {
  return(x %*% t(x))
}
polyK <- function(x, d=2) {
  return((1 + plainK(x))^d)
}
gaussK <- function(x, sigma=1) {
  n = nrow(x)
  K = matrix(0, nrow=n, ncol=n)
  for (i in 1:n) {
    for (j in 1:n) {
      K[i, j] = -sum((x[i]-x[j])^2)
    }
  }
  K = exp(K / sigma)
  return(K)
}
kernel_pca <- function(K, data) {
  N <- dim(K)[1]
  # center K
  K_centered <- (diag(N) - (1/N))%*%(K)%*%(diag(N) - (1/N))
  #
  # calculate eigenvalues and eigenvectors of K/N
  result <- eigen(K_centered)
  
  eval2 <- result$values[c(1:3)]
  PC2 <- result$vectors[, c(1,3)]
  # calculate PC scores
  PC_scores <- K_centered %*% PC2
  kernel_PCA_prjtn = data.frame(PC_scores, class = data$Toast_final)
  # (ggplot(data = kernel_PCA_prjtn, aes(x = kernel_PCA_prjtn[,c(1)],
  # y = kernel_PCA_prjtn[,c(2)]))
  # + geom_point(aes(color=class))
  # + labs(title = "Projection onto PC1 and PC2", x = "PC1", y = "PC2"))
  
  plot_ly(x=kernel_PCA_prjtn[,c(1)], y=kernel_PCA_prjtn[,c(2)], z=kernel_PCA_prjtn[,c(3)], type="scatter3d", mode="markers", color=feature_table_wide4$Toast_final, title = "Projection onto PC1, PC2, PC3")
  return(kernel_PCA_prjtn)
}
```
```{r}
# Choose your kernel
plain_K = plainK(as.matrix(features_only))
kernel_pca(plain_K, feature_table_wide4)
```


```{r}
poly_K = polyK(as.matrix(features_only), 2)
kernel_pca(poly_K, feature_table_wide4)
```
Data separable with 3 PCs, plain_K, polynomial kernal

```{r}
gauss_K = gaussK(as.matrix(features_only), 1)
kernel_pca(gauss_K, feature_table_wide4)
```
Gaussian kernel really doesn't separate the Toast classes.

Hard to separate CE vs. no CE; will create binary label for now

```{r}
# responseY = feature_table_wide4$Toast_final
# 
# myvars <- names(feature_table_wide4) %in% c("EMPI","stroke_date_index","Toast","CCS",
#                                            "Toast_new","Toast_final")
# predictorX <- feature_table_wide4[!myvars]
# 
# # scaling -> cor=T; no scaling -> F
# pca = princomp(predictorX, cor=F)
# 
# pc.comp = pca$scores
# pc.comp1 = -1*pc.comp[,1] # principal component 1 scores (negated for convenience)
# pc.comp2 = -1*pc.comp[,2] # principal component 2 scores (negated for convenience)
# plot(pc.comp1, pc.comp2, xlim=c(-2,1), ylim=c(-2,1), type="n")
# points(pc.comp1[responseY==0], pc.comp2[responseY==0], cex=0.5, col="blue")
# points(pc.comp1[responseY==1], pc.comp2[responseY==1], cex=0.5, col="red")
```


```{r}
# Followed this tutorial
# https://uc-r.github.io/hc_clustering

# install.packages("factoextra", repos = "http://cran.cnr.berkeley.edu/")
# install.packages("dendextend", repos = "http://cran.cnr.berkeley.edu/")
library(tidyverse)  # data manipulation
library(cluster)    # clustering algorithms
library(factoextra) # clustering visualization
library(dendextend) # for comparing two dendrograms

# Hierarchical clustering with dendrograms
## try hclust to identify new groups
# using distance matrix

features_only <- subset(feature_table_wide4, select = -c(EMPI,Toast,CCS,stroke_date_index, Toast_new, age, Gender, Toast_final))
d <- dist(features_only, method = "euclidean")

# Hierarchical clustering using Complete Linkage
hc1 <- hclust(d, method = "complete" )

# Plot the obtained dendrogram
plot(hc1, cex = 0.6, hang = -1)

# Compute with agnes
hc2 <- agnes(features_only, method = "complete")

# Agglomerative coefficient
hc2$ac
# measures the amount of clustering structure found (values closer to 1 suggest strong clustering structure
```
Strong clustering structure, suggests random forest may be useful


```{r}
# methods to assess
m <- c( "average", "single", "complete", "ward")
names(m) <- c( "average", "single", "complete", "ward")

# function to compute coefficient
ac <- function(x) {
  agnes(features_only, method = x)$ac
}

map_dbl(m, ac)
```
Here we see that Ward’s method identifies the strongest clustering structure of the four methods assessed.
ward = 0.9985450

```{r}
hc3 <- agnes(features_only, method = "ward")
pltree(hc3, cex = 0.1, hang = -1, main = "Dendrogram of agnes")
```
Can split the data mainly by 2-3 variables

```{r}
# Ward's method
hc5 <- hclust(d, method = "ward.D2" )

# Cut tree into 5 groups
sub_grp <- cutree(hc5, k = 3)

# Number of members in each cluster
table(sub_grp)
```

```{r}
features_only_cluster <- features_only %>%
  mutate(cluster = sub_grp)
```

```{r combo_features_freq}
combo_features_freq_fn <- function(data) {
  data <- data %>% dplyr::select(-cluster)
  combos <- data %>% unite(combo,sep = "", remove = F)
  combos <- combos %>% dplyr::select(combo) %>% unlist()
  combos_freq <- table(combos)
  
  ret <- sort(combos_freq, decreasing = T)
  return(ret)
}
```

```{r}
for (i in 1:3) {
  print("combos")
  # print(combo_features_freq_fn(features_only_cluster[features_only_cluster$cluster == i,]))
  combo <- combo_features_freq_fn(features_only_cluster[features_only_cluster$cluster == i,])[1]
  print(get_combo_name(names(combo)))
  
}


```
important variables in order of greatest to least importance: af, then chf

```{r}
plot(hc5, cex = 0.02)
rect.hclust(hc5, k = 3, border = 2:5)
```

```{r}
fviz_cluster(list(data = features_only, cluster = sub_grp))
```
A lot of overlap between af vs af-chf clusters

```{r}
fviz_nbclust(features_only, FUN = hcut, method = "wss")
```
2-3 seem to be the optimal number of clustes
```{r}
fviz_nbclust(features_only, FUN = hcut, method = "silhouette")
```
```{r}
gap_stat <- clusGap(features_only, FUN = hcut, nstart = 25, K.max = 10, B = 50)
fviz_gap_stat(gap_stat)
```

```{r}
k2 <- kmeans(features_only, centers = 10, nstart = 25)
str(k2)
fviz_cluster(k2, data = features_only)
```
There are interesting clustering properties.


```{r}
k2 <- kmeans(features_only, centers = 10, nstart = 25)
k2
fviz_cluster(k2, data = features_only)
```



